Verifying Demonstrations

### 2019-02-19 paper/location-proofs.tex
Removes DB from location-proofs

\subsection{Location proofs}

Some \acp{LBS} only grant access to resources to users located at a particular 
location, thus raising the issue of verifying the position claimed by a 
particular user.
In most of the existing schemes, the location of a user (device) is determined 
by the device itself (\eg through GPS) and forwarded to the \ac{LBS} provider.
One of the main drawbacks of this approach is that a user can cheat by having 
her device transmit a false location.
Therefore, it is possible for a user to be inappropriately granted access to a 
particular resource while being thousands of kilometers away.

>>>>

\subsection{Distance bounding and location proofs}
\label{db-and-lp}
Some \acp{LBS} only grant access to resources to users located at a particular 
location, thus raising the issue of verifying the position claimed by a 
particular user.
In most of the existing schemes, the location of a user (device) is determined 
by the device itself (\eg through GPS) and forwarded to the \ac{LBS} provider.
One of the main drawbacks of this approach is that a user can cheat by having 
her device transmit a false location.
Therefore, it is possible for a user to be inappropriately granted access to a 
particular resource while being thousands of kilometers away.
